### 2018-08-27 paper/abstract.tex
small changes to introduction
Abstract updated to a shorter version

In this paper, new contributions to testing Communicating Sequential
Processes (CSP) are presented, with focus on the generation of complete,
finite test suites. A test suite is complete if it can uncover every
conformance violation of the system under test with respect to a reference
model. Both reference models and implementation behaviours are represented as
CSP processes. As conformance relation, we consider trace equivalence and
trace refinement, as well as failures equivalence and failures refinement.
Complete black-box test suites here rely on the fact that the SUT's true
behaviour is represented by a member of a fault-domain, that is, a collection
of CSP processes that may or may not conform to the reference model. We
define fault domains by bounding the number of excessive states occurring in
a fault domain member's representation as a normalised transition graph, when
comparing it to the number of states present in the graph of the reference
model. This notion of fault domains is quite close to the way they are
defined for finite state machines, and these fault domains guarantee the
existence of {\it finite} complete test suites.

>>>>

In this paper, two new contributions for model-based testing  
with   Communicating Sequential Processes (CSP) are presented. 
For a given CSP process representing the reference model, test suites 
checking the conformance relations 
trace refinement and  failures refinement are constructed, and their finiteness
and completeness (i.e. capability to uncover conformity violations) is proven. While complete test suites for CSP processes have been previously investigated by several authors, a sufficient condition for their finiteness is presented here for the first time. Moreover, an optimal technique for
testing the admissibility of an implementation's nondeterministic behaviour is described.
